---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lighting

<!-- badges: start -->
<!-- badges: end -->

The goal of lighting is to provide some tools to manipulate data, which are used in the lighting industry. These tools can be categorised into:

- light distribution
- light spectrum and lighting quantities (under development)

## Installation

You can install the development version of lighting from [GitHub](https://github.com/Wei-Lim/lighting/) with:

``` r
# install.packages("devtools")
devtools::install_github("Wei-Lim/lighting")
```

## Example

### Read LDT file

Reads LDT into a specific light distribution list. For list items definitions see `?ld_data`.

```{r example}
library(lighting)

# typical ldt-file (min. example)
file <- system.file('extdata', "ldt_min_example.ldt", package = "lighting")

# specific light distribution
ld_list <- read_ldt(file)

ld_list
```

### Plot light distribution (polar chart)

Plots a typical light distribution data.
<p>
```{r}
plot_light_distribution(ld_list$lum_int_extended_tbl)
```
</p>
### Write LDT, convert to IES and export to SVG
```{r eval=FALSE}
# Write LDT 
ld_write_ldt(ld_list)

# Write IES
ld_write_ies_lm63_2002(ld_list)

# Write SVG			 
ld_write_svg(ld_list)			 
```

